Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-06-09 numerical-zeus.tex
Use breakurl package to prevent the bitbucket url from overflowing into the margin.

\subsection{The \zeus\ hydro method}
\label{sec.hydro.zeus}

@@

A limitation of a technique that uses an artificial viscosity is that, while the correct Rankine-Hugoniot jump conditions are achieved, shocks are broadened over 3-4 mesh cells and are thus not treated as true discontinuities. This may cause unphysical pre-heating of gas upstream of the shock wave, as discussed in \citet{1994ApJ...429..434A}.  On the other hand, it is much more robust than PPM and is easy to add additional physics.  We also note that this method solves only the internal energy equation rather than total energy, so the `dual energy formulation' discussed in Section~\ref{sec.hydro.ppm} is unnecessary.

>>>>

\subsection{Hydrodynamics: The \zeus\ method}
\label{sec.hydro.zeus}

@@

A limitation of a technique that uses an artificial viscosity is that, while the correct Rankine-Hugoniot jump conditions are achieved, shocks are broadened over 3-4 mesh cells and are thus not treated as true discontinuities. This may cause unphysical pre-heating of gas upstream of the shock wave, as discussed in \citet{1994ApJ...429..434A}.  On the other hand, it is much more robust than PPM and is easy to add additional physics.  We also note that this method solves only the internal energy equation rather than total energy, so the ``dual energy formulation'' discussed in Section~\ref{sec.hydro.ppm} is unnecessary.
